% this file is part of the smartcard project

\documentclass[letterpaper,12pt]{article}
\setlength{\headheight}{0ex}
\setlength{\headsep}{0ex}
\input{hogg_nasa}
\pagestyle{empty}
\begin{document}

\paragraph{Daniel Foreman-Mackey} http://dan.iel.fm

\paragraph{Education:}~\\[3pt]
\begin{tabular}{llll}
\textsl{undergrad.}
  & McGill University, Montr\'eal, QC, Canada & Physics & BSc 2008\\
\textsl{graduate}
  & Queen's University, Kingston, ON, Canada & Physics & MSc 2010\\
\textsl{graduate}
  & New York University, New York, NY, USA & Physics & PhD expected 2015
\end{tabular}

\paragraph{Honors:}
$\bullet$~James Arthur Graduate Fellowship (2014);
$\bullet$~Horizon Fellowship in the Natural \& Physical Sciences (2012);
$\bullet$~Henry M. MacCracken Fellowship (2010);
$\bullet$~NSERC Undergraduate Summer Research Award (2007).

\paragraph{Publications:}
\begin{itemize}\setlength{\itemsep}{0pt}
\item
Ambikasaran,~S., Foreman-Mackey,~D., Greengard,~L., Hogg,~D.~W., \& O'Neil,~M.,
{Fast direct methods for Gaussian Processes and the analysis of NASA \Kepler\
Mission Data},
\textit{IEEE Transactions on Pattern Analysis and Machine Intelligence},
submitted (\textit{arXiv}:{1403.6015}).
\item
Dawson, R.~I., Johnson, J.~A., Fabrycky, D.~C., Foreman-Mackey, D.,
Murray-Clay, R.~A. \etal,
{Large orbital eccentricity, low mutual inclination},
\textit{Astrophys.\,J.}, submitted.
\item
Dorman, C.~E., Widrow, L.~M., Guhathakurta, P., Seth, A.~C., Foreman-Mackey,
D. \etal, 2013,
{A New Approach to Detailed Structural Decomposition from the SPLASH and PHAT
Surveys: Kicked-up Disk Stars in the Andromeda Galaxy?},
\textit{Astrophys.\,J.}, \textbf{779}, 103.
\item
Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J., 2013,
emcee: The MCMC Hammer, \textit{Pubs.\,Astron.\,Soc.\,Pac.}\ \textbf{125}, 306.
\item
Brewer, B.~J., Foreman-Mackey, D., \& Hogg, D.~W.\ 2013,
{Probabilistic Catalogs for Crowded Stellar Fields},
\textit{Astron.\,J.}, \textbf{146}, 7.
\item
Weisz,~D.~R., Fouesneau,~M., Hogg,~D.~W., \etal, 2013,
{The Panchromatic Hubble Andromeda Treasury. IV. A Probabilistic Approach to
Inferring the High-mass Stellar Initial Mass Function and Other Power-law
Functions},
\textit{Astrophys.\,J.},\ \textbf{762}, 123.
\end{itemize}

\paragraph{Relevant expertise and accomplishments:}
\begin{itemize}\setlength{\itemsep}{0pt}
\item
Lead developer and architect of several popular and open source projects,
including
\emph{(a)} \project{emcee} (http://dan.iel.fm/emcee) user friendly and
high-performance Markov chain Monte Carlo sampling in Python,
\emph{(b)} \project{George} (https://github.com/dfm/george) a C++ library for
efficient Gaussian process regression,
\emph{(c)} \project{triangle.py} (https://github.com/dfm/triangle.py) a Python
module for displaying the results of Markov chain Monte Carlo experiments, and
\emph{(d)} \project{kplr} (https://github.com/dfm/kplr) Python interface
to the Mikulski Archive for Space Telescopes repository of Kepler observations.
\end{itemize}

\end{document}
